\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-07-09 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
adding IEEE 14 bus sim results

\begin{figure}[tb]
\centering
\includegraphics[width=0.9\linewidth]{ProxSchmatic.pdf}
\caption{\small{A schematic of approximating the flow of the joint PDF trajectory $\rho(t,\bm{x})$ via the sequence $\{\varrho_{k}\}_{k\in\mathbb{N}}$ generated by a variational recursion over $\mathcal{P}_{2}\left(\mathbb{T}^{n}\times\mathbb{R}^{n}\right)$. The curve $\rho(t,\bm{x})$ solves a kinetic Fokker-Planck PDE initial value problem. While the joint PDFs are supported over the finite dimensional base manifold $\mathbb{T}^{n}\times\mathbb{R}^{n}$, the proximal updates $\{\varrho_{k}\}_{k\in\mathbb{N}}$ (shown as circled markers with no face-color) evolve over the infinite dimensional manifold $\mathcal{P}_{2}\left(\mathbb{T}^{n}\times\mathbb{R}^{n}\right)$.}}
\vspace*{-0.1in}
\label{fig:ProxSchematic}
\end{figure}

@@

\subsection{IEEE 14 Bus System}\label{subsec:NumSimIEEEBus}
We consider the Kron-reduced dynamics \eqref{ItoSDEcomponentlevel} for the IEEE 14 bus system shown in Fig. \ref{fig:Motivating}. In this case, we have $n=5$ nodes which correspond to the buses 1, 2, 3, 6 and 8 in Fig. \ref{fig:Motivating}. We obtained the parameters of the 14 bus system from MATPOWER \cite{zimmerman2010matpower}. The calculation of Kron-reduced admittance matrix and current vector in \eqref{DefParam} followed Sec.  \ref{subsec:samplepathdynamics}; see also \cite{dorfler2012kron}. The parameters $m_{i}, \gamma_{i}$ are obtained from the open-source Python-based
library ANDES \cite{cui2021andes}.

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=0.9\linewidth]{ProxSchmatic.pdf}
\caption{\small{A schematic of approximating the flow of the joint PDF trajectory $\rho(t,\bm{x})$ via the sequence $\{\varrho_{k}\}_{k\in\mathbb{N}}$ generated by a variational recursion over $\mathcal{P}_{2}\left(\mathbb{T}^{n}\times\mathbb{R}^{n}\right)$. The curve $\rho(t,\bm{x})$ solves a kinetic Fokker-Planck PDE initial value problem. Points on this curve (shown as three filled circled markers at three specific instances $t_0,t_1,t_2$) are joint PDFs. While the joint PDFs are supported over the finite dimensional base manifold $\mathbb{T}^{n}\times\mathbb{R}^{n}$, the proximal updates $\{\varrho_{k}\}_{k\in\mathbb{N}}$ (shown as circled markers with no face-color) evolve over the infinite dimensional manifold $\mathcal{P}_{2}\left(\mathbb{T}^{n}\times\mathbb{R}^{n}\right)$.}}
\vspace*{-0.1in}
\label{fig:ProxSchematic}
\end{figure}

@@

\subsection{IEEE 14 Bus System}\label{subsec:NumSimIEEEBus}
We consider the Kron-reduced dynamics \eqref{ItoSDEcomponentlevel} for the IEEE 14 bus system shown in Fig. \ref{fig:Motivating}. In this case, we have $n=5$ nodes which correspond to the buses 1, 2, 3, 6 and 8 in Fig. \ref{fig:Motivating}. We obtained the parameters of the 14 bus system from MATPOWER \cite{zimmerman2010matpower}. The calculation of Kron-reduced admittance matrix and current vector in \eqref{DefParam} followed Sec.  \ref{subsec:samplepathdynamics}; see also \cite{dorfler2012kron}. The parameters $m_{i}, \gamma_{i}$ were obtained from the open-source Python-based
library ANDES \cite{cui2021andes}.
